---
title: "fars_functions"
author: "revirier"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is an test vignete for the package fars_functions of the Coursera Building R Packages

## Funcions

The fars_functions package contains some functions to read FARS files, summarize and plot the data

The functions included are:
 
 * fars_read  This simple function read a FARS datafile located in the default directory
 * fars_read_years Filter the FARS data for the years passed as a list and return a dataframe with two columns: MONTH and YEAR
 * fars_summarize_years Summarize the rows of FARS data by year and month
 * fars_map_state Show a plot a map with the year's accidents in a state
 
## Example

For example to load a far file we can use the fars_read funcion:

```{r}
require(testpackage)
fars_read("../data/accident_2013.csv.bz2")
```

Summarize the data with the fars_summarize_years function

```{r}
require(dplyr)

fars_summarize_years(c("2013"))
```

And plot a map with the accidents:

```{r}
fars_map_state(10,2013)
```

